Detection of Treatment-Subgroup Interactions in Clustered Datasets with Generalized Linear Mixed-effects Model Trees (GLMM trees)

### 2015-08-28 pkg/glmertree/paper/treatment_interactions.Rnw
git-svn-id: svn://svn.r-forge.r-project.org/svnroot/partykit@763 255f4249-2263-4417-b1ea-8498779e27a7

\vspace{5pt}
\noindent \hangindent=4em Step 1: Set $r = r+1$. Estimate GLM tree ($x_{i}^{\top}\hat{\beta}_{j(r)}$) using $z_{i}^{\top}\hat{b}_{(r-1)}$ as an offset.

\vspace{5pt}
\noindent Step 2: Estimate random effects $z_{i}^{\top}\hat{b}_{(r)}$ using $x_{i}^{\top}\hat{\beta}_{j(r)}$ as an offset.

>>>>

\vspace{5pt}
\noindent \hangindent=4em Step 1: Set $r = r+1$. Estimate GLM tree ($x_{i}^{\top}\hat{\beta}_{j(r)}$), with $z_{i}^{\top}\hat{b}_{(r-1)}$ as an offset.

\vspace{5pt}
\noindent Step 2: Estimate random effects $z_{i}^{\top}\hat{b}_{(r)}$, with $x_{i}^{\top}\hat{\beta}_{j(r)}$ as an offset.
